---
title: "shinydemo"
author: "Kate Seeger"
date: "11/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(shiny)
# If you need to install my gardenR library
# library(devtools)
# devtools::install_github("llendway/gardenR")
library(gardenR) # yay, my garden data again!
library(tidyverse)
library(DT) # for table output

veggies <- garden_harvest %>% 
  distinct(vegetable) %>% 
  arrange(vegetable) %>% 
  pull(vegetable)


garden_graph <- garden_harvest  %>%
  group_by(date, vegetable) %>%
  summarize(sum_veg = sum(weight)) %>%
  filter(vegetable %in% c("beets", "carrots", "potatoes", "radish", "onions", "rutabaga")) %>%
  ggplot(aes(x = date, y = sum_veg, fill = vegetable)) + geom_boxplot() 

shinygraph<- garden_harvest %>%
 filter(vegetable %in% c("beets",
                                           "carrots",
                                        "potatoes", 
                                                 "radish", 
                                                 "onions", 
                                                 "rutabaga")) %>%
  group_by(date, vegetable) %>%
  summarize(sum_veg = sum(weight))


shinygraph %>%
  filter(date == "2020-06-21") %>%
  mutate(vegetable = as.factor(vegetable), 
         sum_veg = as.integer(sum_veg)) %>%
      ggplot(aes(sum_veg, fill = vegetable)) +
      geom_histogram(position = "dodge") +
      labs(title = paste("Sum weight (g) of root vegetables on "),
           x = "",
           y = "") +
      theme_minimal()

                                
```

library(shiny)
# If you need to install my gardenR library
# library(devtools)
# devtools::install_github("llendway/gardenR")
library(gardenR) # yay, my garden data again!
library(tidyverse)
library(DT) # for table output

veggies <- garden_harvest %>% 
  distinct(vegetable) %>% 
  arrange(vegetable) %>% 
  pull(vegetable)

# Define UI for application 
ui <- fluidPage(
  # Application title
  titlePanel("Root Veggies Harvested From Lisa's Garden"),
  

  # Sidebar with inputs 
  sidebarLayout(
    sidebarPanel(
      #this is for box/bar/point plot
      # dateInput(inputId = "date", 
      #           label = "Date of Harvest", 
      #           value = "2020-06-06"
      #           ),
      selectInput(inputId = "veg", # to use in code
                  label = "Vegetable:", # how it looks in UI
                  choices = veggies, 
                  selected = "tomatoes"
      ),
      sliderInput(inputId = "date", 
                  label = "Date Range: ",
                  min = min(garden_harvest$date), 
                  max = max(garden_harvest$date), 
                  value = c(min(garden_harvest$date),
                            max(garden_harvest$date)),
                            )
      
      
    ),
    
    # Show a plot of cumulative weight for chosen vegetable
    # Show a table beneath
    mainPanel(
      plotOutput(outputId = "sum_veg"),
      dataTableOutput(outputId = "sum_veg_tbl")
    )
  )
)

# Define server logic 
server <- function(input, output) {
  
  # First, try this. It WILL NOT work :(    
  # veg_smry <- garden_harvest %>% 
  #     filter(vegetable == input$veg) %>% 
  #     group_by(date) %>% 
  #     summarize(daily_wt = sum(weight)) %>% 
  #     mutate(cum_wt = cumsum(daily_wt))
  
  # Enclose in reactive() - makes a function
  veg_smry <- reactive(garden_harvest %>%
                         # filter(vegetable %in% c("beets",
                         #                         "carrots",
                         #                         "potatoes", 
                         #                         "radish", 
                         #                         "onions", 
                         #                         "rutabaga")) %>%
                         group_by(date, vegetable) %>%
                         summarize(sum_veg = sum(weight)) %>%
                         mutate(cum_wt = cumsum(sum_veg))
  )
                       
  
## THIS IS FOR BOXPLOT?BAR?POINTPLOT
  
#   # Now use that function, with no arguments.
#   output$sum_veg <- renderPlot({
#     veg_smry() %>% 
#       filter(date == input$date) %>%
#       ggplot(aes(x = vegetable, y = sum_veg, fill = vegetable)) +
#       geom_boxplot() +
#       labs(title = paste("Sum weight (gram) of root vegetables on ", input$date),
#            x = "",
#            y = "") +
#       theme_minimal()
#   })
#   
#   output$sum_veg_tbl <- renderDataTable(veg_smry())
#   
# }


# Now use that function, with no arguments.
output$sum_veg <- renderPlot({
  veg_smry() %>% 
    filter(vegetable == input$veg)
    ggplot(aes(x = vegetable, y = sum_veg, fill = vegetable)) +
    geom_boxplot() +
    labs(title = paste("Sum weight (gram) of root vegetables on ", input$date),
         x = "",
         y = "") +
    theme_minimal()
})

output$sum_veg_tbl <- renderDataTable(veg_smry())

}

# Run the application 
shinyApp(ui = ui, server = server)
